\documentclass{article}

\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{url}

%\usepackage{placeins}
%\usepackage{algorithm}
%\usepackage{algorithmic}

\renewcommand{\vec}[1]{\boldsymbol{#1}}
\newcommand{\mat}[1]{\mathtt{#1}}
\newcommand{\ten}[1]{\mathcal{#1}}
\newcommand{\crossmat}[1]{\begin{bmatrix} #1 \end{bmatrix}_{\times}}
\newcommand{\class}[1]{{\cal C}_{#1}}
\def\Rset{\mathbb{R}}
\def\Pset{\mathbb{P}}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\sign}{sign}
\def\norm{\mbox{$\cal{N}$}}

\newcommand\parms{\vec{\theta}}
\newcommand\oldparms{\parms^{\text{old}}}

\title{Test}
\author{Kan Ouivirach}

\textwidth 6in
\oddsidemargin 0.35in
\topmargin -0.5in
\textheight 8.5in

\begin{document}

\bibliographystyle{plain}

\maketitle

This write up is for ...

\section{Introduction}
\label{intro}

test reference \cite{koller}

\section{Methods}

xxx


Agile Product Management

tinyPM helps you with agile product management from vision to
implementation. Build your product backlog with user stories and work
iteratively to deliver it.  learn more » No Dogma!

tinyPM does not imply any particular methodology, but gives you well
known element like iterations, user stories and leaves the choice how
to use them to You.  learn more » Distributed Collaboration

tinyPM supports collaboration within distributed teams and it does it
for real! Share project knowledge, leave comments and get notified
whenever your team mates respond.  learn more » Ease of Use

Tiny effort, perfect management is our mantra. This means that we
build the tool as easy to use as possible. This way tinyPM is so well
accepted by your devs, business and clients.

\section{Results}

xxx

\section{Conclusions}

xxx

%\FloatBarrier

\bibliography{references} % use data in file "references.bib"

\end{document}


